---
title: "Cabbages"
author: "Joel Calderin"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
library(ggplot2)
library(dplyr)

veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$ There is no difference in the vitamin C content of cabbages based on cultivation method.

$H_A$ There is a difference in the vitamin C content of cabbages based on the cultivation method.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
data = veggy
```

Vitamin C content is a numerical variable, and cultivation method is a categorical variable. Therefore, we use the Numerical-Cat helper file.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
ggplot(data, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "Cult", y = "VitC") +
  theme_minimal()

```

The box plot shows that there is a difference in vitamin C content in method C52 and C39. The median of vitamin C in C52 is higher than the median of vitamin C in C39 by around 15 IUs. 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
num_summary <- data %>%
  group_by(Cult) %>%
  summarise(
    Mean = mean(VitC),
    Median = median(VitC),
    SD = sd(VitC)
  )

num_summary

```

Cultivation method 39 has a mean of 51.5 vitamin C content, while cultivation method 52 has an mean of 64.4 vitamin C content.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
 t.test(VitC ~ Cult, data = data)

```


The p value is equal to 0.00000003405. This p value is lower than 0.05, so we reject the null hypothesis. This means that there is a difference in the average number of vitamin C in mehtod C39 and C52

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


The original question was if there was a difference in the average vitamin C content in cultivation method 39 and method 52? There is indeed a difference. We can see this in our numerical and graphical results; as it shows the average vitamin C in C39 was 51.5, and C52 was 64.4. We can also find that there is a difference in our P value, as it was lower than 0.05, so we rejected the null hypothesis. 
In conclusion, cultivation method 52 provided more vitamin C in the cabbages on average compared to cultivation method 39. 